### 2023-05-14 doc/Thesis/chapter/063-discussion.tex
delete unnecessary files and rearange folder structure

\section{Hindsight is easier than foresight}
%\section{Discussion}
%\todo{search i.e. and replace with i.e.\ }
%\todo{go to experimental and material (IV) discussion}
%\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer. resistance of steel is neglectable. In order to get an impression of the quality of the layer mutliple contact (picture) are sputtered (throuhg a mask) and statistics: Two angabewerte: the weighted durchschnit and the number of pinholes, ie the number of contacts which were shorted, have an resistance below an threshold. if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
%\todo{go to anova discussion}
%- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
%\todo{british or US?: zation vs zation} 
%\todo{ include last phase into previous section}
This section will discuss mistakes, improvements and lessons learned for each phase of this project in chronological order. 
Firstly, the 
\ref{sec:phase1} \textit{\nameref{sec:phase1}}%
, followed by the 
\ref{sec:phase2} \textit{\nameref{sec:phase2}}%
%, thereupon the 
 and finally the 
\ref{sec:phase3} \textit{\nameref{sec:phase3}}%
%\ref{sec:phase3} \textit{\nameref{sec:phase4}}%
 will be discussed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Research, exploration and design phase}
\label{sec:phase1}
%\td{freewriting}: 
\textbf{Scrutinize everything!} At the beginning of a project it is important 
to get a ``feel''. I took the first recipe as only true recipe and tried to tune it to perfection. 
The problem was that the base line of that recipe was so low such that no matter how much I improved it, it was still bad. 
I only noticed this after trying out another recipe. 
My tip here is to read as much and mostly diverse literature as possible and then try to mimic what ever you can. 
This will get you a ``feel'' of what works and what does not. 
Thinking back to some design classes I took for data visualization: create as many and different designs as possible. 
Check what works, collect (dis-)advantages of methods and combine the best approaches. 
This can save you a lot of time.

@@

Another step/deed which is well placed in this phase is the estimate the error by reproducing a single sample a certain number of times. 
%Where the number will then be higher than during optimization 
%\todo{include curse of dimensionality.}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Optimization, modelling and data generation}
\label{sec:phase3}
During the optimization the main problems were too many in- and output variables, reproducibility and regularization. 
%The first problem 
Variable selection has already been discussed in the previous section. 
When working with stochastic algorithms it is especially important to introduce reproducibility via a seed, which determines all subsequent pseudo-random numbers. 
Finally, during the \gls{emma} optimization the input data were not regularized, %es wurde auf regularization verzichtet, 
because the regularization would be different for different generations.
Regularizing with the mean and standard deviation would be either inconsistent across generations or over overvalue the distribution of the initial generation. 
%because the distribution of 
%
%alter previous measurements, which alread beitragen to the model and the influence the decision of the next sample. 
These were the reasons for not including regularization during \gls{emma} optimization. 
On the other hand the input data could have been regularized to only take values $[-1;1]$ by defining the regularized varible as 
$x'= \frac{x-\bar{x}}{x_{max} - \bar{x}}$ with $\bar{x}= x_{\text{max}} - x_{\text{min}}$.
%On the other hand haette man auf jeden fall die input variablen normieren können. 
%Normally, for standardization the mean is substracted and it is devided by the standard deviation, which impplies a distribution of a random variable. 
%One could have assumed a standard uniform distribution. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
\iffalse
\begin{itemize}
    \item regularization
    \item reproducability (random in code and repeat sample)
    \item main problems too many in and output vars
%\td{two main problems: 1. too many input variables; 2. too many output varibales; at2: as some input variables were also output variables, MARS couldnt find correct BFs. This could be used though: use input var also as output var if you think they are inportant, this way they will be more likely to be choosen in basis function}
\end{itemize}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\subsection{Evaluation, interpretation and outlook phase}
\label{sec:phase4}
\begin{itemize}
    \item why lowest $\gamma$ for lowest $T_{cal}$? according which eq? emma? 
    \item why $\gamma ~ \lambda$? (minimum for layer count?) according which eq? emma? 
    \item reasons for large error per sample: ageing of solution, varying humidity, varying room temperature?, impurities in solutions, inhomogeneity of film, measureing error, systematical/thinking error? what else? 
%What is the reason for aging (O2,H2O?, not sealing accelerates) ? 
%Why does \gls{ipo} decelerate the aging process? ( ipo fits better to solvent(buoh)?)
%the original solvent was 2-methoxy-ethonanol instead of \ch{buoh}.
%\td{COMMENT: solution age was not accounted for}
    \item \td{maybe the lowering of G and p are not because of better process variables but because of me getting better at creating the layers *sad* :0 } 
\end{itemize}
\fi

>>>>

\section{Hindsight is easier than foresight}
%\section{Discussion}
%\todo{search i.e. and replace with i.e.\ }
%\todo{go to experimental and material (IV) discussion}
%\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer. resistance of steel is neglectable. In order to get an impression of the quality of the layer mutliple contact (picture) are sputtered (throuhg a mask) and statistics: Two angabewerte: the weighted durchschnit and the number of pinholes, ie the number of contacts which were shorted, have an resistance below an threshold. if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
%\todo{go to anova discussion}
%- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
%\todo{british or US?: zation vs zation} 
%\todo{ include last phase into previous section}
This section will discuss mistakes, improvements and lessons learned from each phase of this project. % in chronological order. 
Firstly,
the \nameref{sec:phase1} will be discussed in subsection \ref{sec:phase1}, 
followed by the \nameref{sec:phase2} reviewd in subsection \ref{sec:phase2} 
%, thereupon the 
and finally the \nameref{sec:phase3} examined in subsection \ref{sec:phase3}.
%\ref{sec:phase3} \textit{\nameref{sec:phase4}}%
% will be discussed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Research, exploration and design phase}
\label{sec:phase1}
%\td{freewriting}: 
\textbf{Scrutinize everything!} At the beginning of a project it is important 
to get a ``feel''. 
I took the first recipe as only true recipe and tried to tune it to perfection. 
The problem was that the base line of that recipe was so low such that 
improving the recipe still lead to poor performance.
%no matter how much I improved it, it was still bad. 
This was only noticed this after trying out another recipe. 
The author's tip here is to read as much and mostly diverse literature as possible and then try to mimic what ever can be. 
This will 
make it possible to acquire 
%get you a 
``feel'' of what works and what does not. 
%Thinking back to some design classes I took with \href{http://www.tomtorsneyweir.com/}{Thomas Torsney-Weir} for data visualization: 
This is inspired by a quote from \href{http://www.tomtorsneyweir.com/}{Thomas Torsney-Weir}'s 
data visualization classes: ``create as many and different designs as possible''.
One should check what works, collect (dis-)advantages of methods and combine the best approaches. 
This can save you a lot of time.

@@

Another step/deed which is well placed in this phase is the estimate the error by reproducing a single sample a certain number of times. 
%Where the number will then be higher than during optimization 
%\todo{include curse of dimensionality.}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Optimization, modelling and data generation phase}
\label{sec:phase3}
During the optimization the main problems were too many in- and output variables, reproducibility and regularization. 
%The first problem 
Variable selection has already been discussed in the previous section. 
When working with stochastic algorithms it is especially important to introduce reproducibility via a seed, which determines all subsequent pseudo-random numbers. 
Finally, during the \gls{emma} optimization the input data were not regularized, %es wurde auf regularization verzichtet, 
because the regularization would be different for different generations.
Regularizing with the mean and standard deviation would be either inconsistent across generations or over overvalue the distribution of the initial generation. 
%because the distribution of 
%
%alter previous measurements, which alread beitragen to the model and the influence the decision of the next sample. 
These were the reasons for not including regularization during \gls{emma} optimization. 
On the other hand the input data could have been regularized to only take values $[-1;1]$ by defining the regularized varible as 
$x'= \frac{x-\bar{x}}{x_{max} - \bar{x}}$ with $\bar{x}= x_{\text{max}} - x_{\text{min}}$.
%On the other hand haette man auf jeden fall die input variablen normieren können. 
%Normally, for standardization the mean is substracted and it is devided by the standard deviation, which impplies a distribution of a random variable. 
%One could have assumed a standard uniform distribution. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
\iffalse
\begin{itemize}
    \item regularization
    \item reproducability (random in code and repeat sample)
    \item main problems too many in and output vars
%\td{two main problems: 1. too many input variables; 2. too many output varibales; at2: as some input variables were also output variables, MARS couldnt find correct BFs. This could be used though: use input var also as output var if you think they are inportant, this way they will be more likely to be choosen in basis function}
\end{itemize}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\subsection{Evaluation, interpretation and outlook phase}
\label{sec:phase4}
\begin{itemize}
    \item why lowest $\gamma$ for lowest $T_{cal}$? according which eq? emma? 
    \item why $\gamma ~ \lambda$? (minimum for layer count?) according which eq? emma? 
    \item reasons for large error per sample: ageing of solution, varying humidity, varying room temperature?, impurities in solutions, inhomogeneity of film, measureing error, systematical/thinking error? what else? 
%What is the reason for aging (O2,H2O?, not sealing accelerates) ? 
%Why does \gls{ipo} decelerate the aging process? ( ipo fits better to solvent(buoh)?)
%the original solvent was 2-methoxy-ethonanol instead of \ch{buoh}.
%\td{COMMENT: solution age was not accounted for}
    \item \td{maybe the lowering of G and p are not because of better process variables but because of me getting better at creating the layers *sad* :0 } 
\end{itemize}
\fi
